Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-11 paper.qmd
Removed unnecessary code chunk in MNIST

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 4
#| fig-width: 12
#| out-width: 100%
#| fig-cap: "\\gD{} wireframe layout shows that there is a big non-linear cluster (grey) and a small cluster (orange) located very close to the one corner of the big cluster. The MNIST digit 1 data ($n =  7877$ and $p = 10$) has a non-linear structure in $10\\text{-}D$. Two \\gD{} projections from a tour on $10\\text{-}D$ reveal that the closeness of the clusters in $10\\text{-}D$ and the twisted pattern of the model fit with tSNE ($a_1 = 0.041$, $b = 659/585 \\text{ } (30, \\text{ }48)$). Video of the langevitour animation is available at <>."
#| eval: false

free(trimesh_removed_mnist) + mnist_proj_tsne_model1 +
  mnist_proj_tsne_model2 +
  plot_layout(ncol = 3)

@@

# Create the table
kable(links_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE) |>
  kable_styling(position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:3, width = c("1cm", "5cm", "9cm"))
```

>>>>

@@

# Create the table
kable(links_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE) |>
  kable_styling(position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:3, width = c("1.5cm", "4.5cm", "9cm"))
```
